---
title: "POL 310: Religion and Politics in the United States"
format:
    html: default
    pdf: 
      documentclass: article
      fontsize: 12pt
      colorlinks: true
      citecolor: DarkViolet
      linkcolor: DarkViolet
      urlcolor: DarkViolet
      geometry: margin=1in
      output-file: "POL310_syllabus"
---

```{r setup, message=FALSE, warning=FALSE, include=FALSE}
library(dplyr)
library(tibble)
library(pander)
```

::: {.content-visible when-format="pdf"}

\begin{center}

\vspace{-5em}

\url{ {{< var course.url >}} } \vspace{-1ex}

{{< var course.time >}} {{< var course.days >}} \vspace{-1ex}

{{< var course.location >}} \vspace{-1ex}

{{< var course.semester >}}

\end{center}


## Instructor

{{< var instructor.name >}} \vspace{-1ex}

Email: [{{< var instructor.email >}}](mailto:{{< var instructor.email >}}) \vspace{-1ex}

Office: {{< var instructor.office >}} \vspace{-1ex}

Office hours: Thursdays 10 am - 12 pm

:::


::: {.content-visible when-format="html"}

::: {.grid .course-details .course-details-smaller}

::: {.g-col-6}
### Course details

- {{< fa calendar >}} &nbsp; {{< var course.days >}}
- {{< fa calendar-alt >}} &nbsp; {{< var course.dates >}}
- {{< fa clock >}} &nbsp; {{< var course.time >}}
- {{< fa location-dot >}} &nbsp; {{< var course.location >}}
:::

::: {.g-col-6}
### Instructor

- {{< fa user >}} &nbsp; [{{< var instructor.name >}}]({{< var instructor.url >}})
- {{< fa university >}} &nbsp; {{< var instructor.office >}}
- {{< fa envelope >}} &nbsp; [{{< var instructor.email >}}](mailto:{{< var instructor.email >}})
- {{< fa university >}} &nbsp; Office hours: Thursdays 10 am - 12 pm
:::

:::



# Syllabus

You can find a PDF version of the syllabus with the weekly schedule on the sidebar of this page.

:::


## Course Overview

This course discusses the ways in which religion and politics intersect in the United States. The topics that will be covered include the relationship between church and state; the connection between an individual's religion (i.e., their beliefs and behavior) and their political attitudes and behaviors; how political candidates make use of religion; churches as political communities; the rise of the "Religious Right" and Christian nationalism; and the intersection of religion and politics for racial, ethnic, and religious minorities. The course will highlight important concepts and theories as well as the measures and data that scholars use to study the influence of religion on American politics.


## Learning Outcomes

- Develop an understanding of the role that America's religious traditions have played in contemporary politics.
- Think critically about the ways in which religion influences politics and politics influences religion.
- Examine the intersection of religion and politics through a social scientific perspective, generating questions and ways to answer them.
- Apply the theories and concepts from religion and politics research to current events.


## Work and Assessment

### Course Expectations

Students are expected to attend class and participate during class discussions. This course has both a lecture and a discussion component. The lectures will incorporate the readings assigned for that day/week. I expected you will have completed all readings prior to class and will come prepared with comments and questions. Readings can be accessed through the library resources or, when not available through the library, via Canvas.

- <ins>*A note of caution:*</ins> many, if not most, of the readings come from academic journals and books, mostly from political science but also from sociology. You will find that many of the articles are quite technical and they can be hard to follow even when one is familiar with the methodology. Do not despair. Make sure to understand, and wrestle with, the main ideas presented in a piece. Pay attention as well to how the authors support their arguments with data without getting bogged down by technical details.

### Course Workload

This is a 4-credit hour course, meaning that you are expected to spend 12 hours of work each week (including the 3 hours spent in the classroom). This roughly means that you will spend about 2 hours on readings for each class period, and 3 hours each week working on the different assignments (pace yourself!).


### Assignments and grades

Final course grades will be assigned as follows:

```{r grades, include=FALSE}
grading <- tribble(
  ~Grade, ~Range, ~Grade1, ~Range1,
  "A",  "93–100%", "C",  "73–76%",
  "A−", "90–92%", "C−", "70–72%",
  "B+", "87–89%", "D+", "67–69%",
  "B",  "83–86%", "D",  "63–66%",
  "B−", "80–82%", "D−", "60–62%",
  "C+", "77–79%", "F",  "< 60%"
)
```

<div class="centered-table">

```{r show-grades-table, echo=FALSE, results="asis"}
grading %>%
  pandoc.table(justify = "lclc",
               col.names = c("Grade", "Range", "Grade", "Range"))
```

<div>


Final grades will be calculated based on the following components:

**Participation (20%)**: All students are expected to be active participants in class discussions. Our learning experience will be enhanced if you come prepared and ready to share your comments, insights, and/or questions from the material covered in the lectures and readings with the rest of the class.

  - <ins>*Attendance policy:*</ins> Attendance is part of your participation grade, and while there is no separate grade for attendance it is a prerequisite for in-class participation. That said, to accommodate unforeseeable circumstances, you have two *unexcused* absences that will not affect your participation grade. Please let the instructor know about any excused absences you anticipate during the semester. Note that students who are absent, whether excused or not, are still expected to submit the weekly summary corresponding to that class period.


**Weekly summaries (15%)**: Each week for eight weeks, you will summarize one article from the week's readings (the reading you can summarize has a {{< fa pen >}} after it in the course schedule). There are  weeks in the semester where you can write a summary, so you can skip some weeks. It is up to you to decide which weeks to skip. The summary must be no longer than three-quarters of a page (single-spaced, 12-point font). These summaries must be submitted on Canvas before class time *on the day the reading was assigned*.


**Campaign memo (15%)**: You will write a campaign memo (4-6 pages, single-spaced) on strategies for religious outreach for a fictitious Senate race. Students must provide sufficient background, provide clear takeaways, and propose strategies for a political campaign to appeal to the religious and non-religious voters. The audience for this paper is a political campaign staff.


**Congregational visit paper (25% total)**: You will write an empirical research paper (4-6 pages, double-spaced) similar to the ones political scientists publish in academic journals. For this assignment, you will attend at least one religious service of a religious tradition or denomination other than your own and will write about how politics is (or is not) addressed, directly or indirectly, in that particular congregation. The paper will be broken down into the following parts that you will submit throughout the semester:

  1. <ins>*Front end of paper (2-3 pages, 5% of final grade):*</ins> This portion of the paper includes the motivation, research questions, literature review, theory, expectations, and methodology. This will be due early in the semester for you to do your best and get feedback.
  
  2. <ins>*Full draft for peer review (4-6 pages, 5% of final grade):*</ins> After collecting data for the paper, you will submit a full draft of the paper for peer review. Another student will provide feedback on your work and you will do the same for them.
  
  3. <ins>*Final draft (4-6 pages, 15% of final grade):*</ins> After the peer review, you will submit the final draft of the paper. I expect you will have included the feedback you received on the first portion of the paper as well as the feedback from your classmate.

- Papers must be submitted via Canvas. Late submissions will be penalized: half a point (out of 10) if turned in late but within 24 hours and one point for each 24-hour period after the due date.


**Exam-style Questions (5% each)**: Throughout the semester, you will answer two exam-style questions. These questions will ask you to explain some class concepts and/or to apply a theoretical framework to answer a substantive question. In addition, these questions will serve as preparation for the final exam where you will answer similar questions.


**Final Exam (15%)**: There will be a final exam where you will answer three medium-length questions. The final exam will take place during the final exam period and will be administered on Canvas. These exams will assess your familiarity with the terms and theories in the religion and politics literature that we will have covered in class.



## Course Conduct

A common saying advises never to discuss politics or religion in polite company. In this class, we will discuss politics *and* religion and we will do so in a respectful environment. As is bound to be the case when we talk about religion, we will discuss many topics that might be controversial or of a sensitive nature for some or all in our group. Our goal in this class is to have constructive discussions about how religion and politics intersect. Derogatory comments toward other students or to members of a particular religious group will not be tolerated.


## Communication Policy

If you have questions about class in general or about a specific assignment, you can email me or come by my office. You can expect a response within 24 hours (unless you email me on Friday). Students are also more than welcome to attend office hours, as this is time set aside specifically for you. In addition, if my office door is open, feel free to stop by. Please note that I will not be "pre-grading" assignments, but I am happy to answer clarifying questions about them either via email or, preferably, during office hours.


## Regrading Policy

If a student wishes to appeal a grade, they must do so in writing within one week of receiving their graded assignment back. The student must indicate clearly what part of the assignment's grading they disagree with, making sure to respond to the instructor's comments in that section and making their case for why they should not have been deducted points. These requests should be done via email and the subject name should read "POL 310 Regrading request - [Name of assignment]." 


## Honor Code

Students are expected to do their own work and cite sources appropriately. Plagiarism will not be tolerated. In other words, students will be held to the standards of the Agnes Scott Honor System to which they agreed when enrolling at this institution. The Agnes Scott College honor code embodies an ideal of character, conduct, and citizenship, and is an important part of the College’s mission and core identity. This applies especially to academic honesty and integrity. Passing off someone else’s work (or Chat GPT's) as your own represents intellectual fraud and theft and violates the core values of our academic community. To be honorable, you should understand not only what counts as academic dishonesty, but also how to avoid engaging in these practices.


You are responsible for the content of any work submitted for this course. The use of artificial intelligence (AI) to generate a first draft of text is permitted, but you must review and revise any AI-generated text before submission. AI text generators can be useful tools but they are often prone to factual errors, incorrect or fabricated citations, and misinterpretations of abstract concepts. I neither encourage nor discourage their use, but utilize them with caution.



## Course Accessibility and Academic Accommodations

Agnes Scott College views disabilities as an integral part of the rich diversity of our community and strives to make all learning experiences as accessible as possible.  If you are a student who receives academic accommodations through the Office of Accessible Education, please schedule a meeting with me within the first two weeks of classes to discuss how your accommodations will be implemented for this course.  During this meeting, you are not expected to disclose any details concerning your disability, though you may discuss these details at your discretion.

If you are a student with a disability---physical, medical, psychological, or learning-specific---and have not connected with Accessible Education to discuss your accessibility needs, please visit the [main Office of Accessible Education webpage](https://www.agnesscott.edu/academicadvising/accessible-education/index.html) to learn more about accommodations, helpful resources and support, available through the Office of Accessible Education.  Students who register for accommodations during the semester should schedule a meeting with me after accommodations have been approved by the Office of Accessible Education.


## Wellbeing and Mental Health

The wellbeing and mental health of students is important; if you are having trouble completing your coursework, please reach out to the [Wellness Center](https://www.agnesscott.edu/wellnesscenter/index.html). Agnes Scott College provides cost-free mental health services to help you manage personal challenges that threaten your personal or academic well-being. If you believe you are experiencing unusual amounts of stress, sadness, or anxiety, please contact the Wellness Center and ask about their [Counseling and Psychological Services](https://www.agnesscott.edu/wellnesscenter/counseling/index.html).


## Title IX

Agnes Scott is here to help you if you have experienced any form of sexual harassment or violence, dating or domestic violence, or stalking. Please talk to any faculty or staff member with whom you feel comfortable. Faculty and staff members want to support you and have been trained to help. They will also inform the Title IX office so that you learn about options available to you. If you do not want college administrators to know what you have experienced, you may talk to the chaplain, as well as nurses or counselors in the Wellness Center with complete confidentiality. They will not tell anyone what you share with them unless you give your express permission. You may contact the Title IX Coordinator directly at <T9Coordinator@agnesscott.edu>.


## Diversity and Inclusion

Agnes Scott is a diverse and inclusive community. As one of the most diverse colleges in the nation, ASC is ideally positioned to be the model of a diverse and inclusive community that society can aspire to be. Such diversity raises the intellectual quality of the classroom experience, creating a unique environment for learning to understand and navigate the challenges of our times. By studying, living, and playing together, Agnes Scott College’s remarkably diverse student body hones the habits of mind, skills, and knowledge essential to ethical and innovative leadership in our increasingly heterogeneous and global society.  As such, this course adheres to the principles of diversity and inclusion as integral to the Agnes Scott community and respects people from all backgrounds. As a first step, this course affirms people’s decisions about gender expression and identity and will use each other’s preferred names and gender pronouns at all times.


## Center for Writing and Speaking

The Center for Writing and Speaking offers one-on-one appointments with trained peer tutors who can help you improve your written and oral communication skills. You are encouraged to use this resource when working on your class assignments to make your arguments more compelling, your sentences clearer, and persistent grammatical errors nonexistent. You can schedule an appointment at <https://www.agnesscott.edu/center-for-writing-and-speaking/index.html>.


## Syllabus Change Policy

This syllabus is only a guide for the course and is subject to change with advanced notice.


::: {.content-visible when-format="pdf"}
  
## Schedule

{{< include content/01-week1.qmd >}}

{{< include content/02-week2.qmd >}}

{{< include content/03-week3.qmd >}}

{{< include content/04-week4.qmd >}}

{{< include content/05-week5.qmd >}}

{{< include content/06-week6.qmd >}}

{{< include content/07-week7.qmd >}}

{{< include content/08-week8.qmd >}}

{{< include content/09-week9.qmd >}}

{{< include content/10-week10.qmd >}}

{{< include content/11-week11.qmd >}}

{{< include content/12-week12.qmd >}}

{{< include content/13-week13.qmd >}}

{{< include content/14-week14.qmd >}}

{{< include content/15-week15.qmd >}}

{{< include content/16-week16.qmd >}}

{{< include content/17-week17.qmd >}}

:::

{{< include index_title.qmd >}}
